manuscript_outline

### 2025-07-14 docs/manuscript/paper.Rmd
re knit everything

---
title: ""
output:  
  bookdown::pdf_document2:
    toc: false
header-includes:
   - \usepackage{lineno}
   - \linenumbers
   - \usepackage{setspace}
   - \doublespacing
csl: methods-in-ecology-and-evolution.csl
bibliography: references.bib
---

@@

**hatchR** requires two core inputs: a vector of daily average water temperatures and a corresponding vector of calendar dates. These data are typically collected from field-deployed temperature loggers. For loggers that record sub-daily temperatures, **hatchR** includes the function `summarize_temp()` to compute daily means. Data completeness and consistency can be checked using `plot_check_temp()` and `check_continuous()` to ensure there are no gaps or anomalies in the temperature record (Table \@ref(tab:eg-temp-data)).

```{r eg-temp-data}
df <- data.frame(
  date = c(
    "2024-01-01",
    "...",
    "2024-07-01",
    "...",
    "2024-12-31"
  ),
  temperature = c(
   4.67,
    "...",
    22.31,
    "...",
    2.58
  )
)

@@

**BMM NOTE: Seems like we should include a figure of output here. Could just add a panel to figure 1 with days to develop plot.**

@@

| Class | Order | Genus | Species | Study |
|:---|:---|:---|:---|:---|
| Amphibia | Anura | *Lithobates* | *L. sylvaticus* | @moore1939 |
|  |  |  | *L. pipiens* |  |
|  |  |  | *L. clamitans* |  |
|  |  |  | *L. palustris* |  |
|  |  | *Ascaphus* | *A. truei* | @brown1975 |
|  | Urodela | *Ambystoma* | *A. gracile* | @brown1976 |
| Reptilia | Squamata | *Sceloporus* | *S. undulatus* | @angilletta2000 |
|  |  | *Podarcis* | *P. mural*is | @vandamme1992 |
|  | Testudines | *Mauremys* | M. reevesii | @du2007 |
|  |  |  | 181 species | 141 studies in @while2018 |
| Insecta | Plecoptera | *Nemurella* | *N. pictetii* | @brittain1978, @elliott1984 |
|  |  | *Capnia* | *C. atra* | @brittain1984 |
|  |  | *Capnia* | *C. bifrons* | @elliott1986 |
|  |  | *Mesocapnia* | *M. oenone* | @brittain1984 |
|  |  | *Taeniopteryx* | *T. nebulosa* | @brittain1977 |
|  | Coleoptera | *Colaphellus* | *C. bowringi* | @tang2017 |
|  |  |  | 18 species | Developmental equations in @pritchard1987 |
| Malacostraca | Decapoda | *Pontastacus* | *P. leptodactylus* | @aydin2004 |
| Copepoda | Calanoida | 10 genera | 28 species | @forster2011 |
|  | Cyclopoida | *Limnoithona* | *L. tetraspina* |  |
|  |  | *Oithona* | *O. davisae* |  |
|  | Harpacticoida | *Microsetella* | *M. norvegica* |  |
|  |  | *Mesochra* | *M.lilljeborgi* |  |
|  | Poecilostomatoida | *Oncaea* | *O. venusta* |  |
| Cephalopoda | Octopoda | *Octopus* | *O. vulgaris* | @márquez2021 |
|  |  |  | *O. mimus* |  |
|  | Myopsida | *Loligo* | *L. vulgaris* |  |
|  |  |  | *L. reynaudii* |  |
|  | Oegopsida | *Illex* | *I. coindetii* |  |
|  |  |  | *I. illecebrosus* |  |
|  |  | *Todarodes* | *T.pacificus* |  |
|  |  | *Ommastrephes* | *O. bartramii* |  |
| Asteroidea | Valvatida | *Odontaster* | *O. meridionalis* | @hoegh-guldberg1995 |
|  |  |  | *O. validus* |  |
|  |  | *Asterina* | *A. miniata* |  |
|  |  | *Acanthaster* | *A. planci* |  |

>>>>

---
title: ""
output:  
  bookdown::pdf_document2:
    toc: false
    number_sections: false
header-includes:
   - \usepackage{lineno}
   - \linenumbers
   - \usepackage{setspace}
   - \doublespacing
csl: methods-in-ecology-and-evolution.csl
bibliography: references.bib
---

@@

**hatchR** requires two core inputs: a vector of daily average water temperatures and a corresponding vector of calendar dates. These data are typically collected from field-deployed temperature loggers. For loggers that record sub-daily temperatures, **hatchR** includes the function `summarize_temp()` to compute daily means. Data completeness and consistency can be checked using `plot_check_temp()` and `check_continuous()` to ensure there are no gaps or anomalies in the temperature record.

```{r eg-temp-data, eval=FALSE}
df <- data.frame(
  date = c(
    "2024-01-01",
    "...",
    "2024-07-01",
    "...",
    "2024-12-31"
  ),
  temperature = c(
   4.67,
    "...",
    22.31,
    "...",
    2.58
  )
)

@@

@@

| Class | Order | Genus | Species | Study |
|:--------------|:--------------|:--------------|:--------------|:--------------|
| Amphibia | Anura | *Lithobates* | *L. sylvaticus* | @moore1939 |
|  |  |  | *L. pipiens* |  |
|  |  |  | *L. clamitans* |  |
|  |  |  | *L. palustris* |  |
|  |  | *Ascaphus* | *A. truei* | @brown1975 |
|  | Urodela | *Ambystoma* | *A. gracile* | @brown1976 |
| Reptilia | Squamata | *Sceloporus* | *S. undulatus* | @angilletta2000 |
|  |  | *Podarcis* | *P. mural*is | @vandamme1992 |
|  | Testudines | *Mauremys* | M. reevesii | @du2007 |
|  |  |  | 181 species | 141 studies in @while2018 |
| Insecta | Plecoptera | *Nemurella* | *N. pictetii* | @brittain1978, @elliott1984 |
|  |  | *Capnia* | *C. atra* | @brittain1984 |
|  |  | *Capnia* | *C. bifrons* | @elliott1986 |
|  |  | *Mesocapnia* | *M. oenone* | @brittain1984 |
|  |  | *Taeniopteryx* | *T. nebulosa* | @brittain1977 |
|  | Coleoptera | *Colaphellus* | *C. bowringi* | @tang2017 |
|  |  |  | 18 species | Developmental equations in @pritchard1987 |
| Malacostraca | Decapoda | *Pontastacus* | *P. leptodactylus* | @aydin2004 |
| Copepoda | Calanoida | 10 genera | 28 species | @forster2011 |
|  | Cyclopoida | *Limnoithona* | *L. tetraspina* |  |
|  |  | *Oithona* | *O. davisae* |  |
|  | Harpacticoida | *Microsetella* | *M. norvegica* |  |
|  |  | *Mesochra* | *M.lilljeborgi* |  |
|  | Poecilostomatoida | *Oncaea* | *O. venusta* |  |
| Cephalopoda | Octopoda | *Octopus* | *O. vulgaris* | @márquez2021 |
|  |  |  | *O. mimus* |  |
|  | Myopsida | *Loligo* | *L. vulgaris* |  |
|  |  |  | *L. reynaudii* |  |
|  | Oegopsida | *Illex* | *I. coindetii* |  |
|  |  |  | *I. illecebrosus* |  |
|  |  | *Todarodes* | *T.pacificus* |  |
|  |  | *Ommastrephes* | *O. bartramii* |  |
| Asteroidea | Valvatida | *Odontaster* | *O. meridionalis* | @hoegh-guldberg1995 |
|  |  |  | *O. validus* |  |
|  |  | *Asterina* | *A. miniata* |  |
|  |  | *Acanthaster* | *A. planci* |  |
